### 2020-01-19 README.Rmd
use `tsk` instead of `mlr_tasks$get()`
Add ResamplingRepeatedSpCVEnv (#32)

| Literature             | Package                                                   | Reference     | Class Name                      | mlr3 Sugar                     |
| ---------------        | ---------                                                 | ---------     | --------------------            | ---------------------          |
| Spatial Buffering      | [blockCV](https://github.com/rvalavi/blockCV)             | Valavi 2019   | `ResamplingSpCVBuffer`          | `rsmp("spcv-buffer")`          |
| Spatial Blocking       | [blockCV](https://github.com/rvalavi/blockCV)             | Valavi 2019   | `ResamplingSpCVBlock`           | `rsmp("spcv-block")`           |
| Spatial CV             | [sperrorest](https://github.com/giscience-fsu/sperrorest) | Brenning 2012 | `ResamplingSpCVCoords`          | `rsmp("spcv-coords")`          |
| Environmental Blocking | [blockCV](https://github.com/rvalavi/blockCV)             | Valavi 2019   | `ResamplingSpCVEnv`             | `rsmp("spcv-env")`             |
| ---                    | ---                                                       | ---           | ---                             | ---                            |
| Repeated Spatial CV    | [sperrorest](https://github.com/giscience-fsu/sperrorest) | Brenning 2012 | `RepeatedResamplingSpCVCoords` | `rsmp("repeated-spcv-coords")` |

@@

| Name     | Code                        | Type    |
| ---      | ---                         | ---     |
| ecuador  | `mlr_tasks$get("ecuador")`  | Classif |
| diplodia | `mlr_tasks$get("diplodia")` | Classif |

>>>>

| Literature             | Package                                                   | Reference     | Class Name                      | mlr3 Sugar                     |
| ---------------        | ---------                                                 | ---------     | --------------------            | ---------------------          |
| Spatial Buffering      | [blockCV](https://github.com/rvalavi/blockCV)             | Valavi 2019   | `ResamplingSpCVBuffer`          | `rsmp("spcv-buffer")`          |
| Spatial Blocking       | [blockCV](https://github.com/rvalavi/blockCV)             | Valavi 2019   | `ResamplingSpCVBlock`           | `rsmp("spcv-block")`           |
| Spatial CV             | [sperrorest](https://github.com/giscience-fsu/sperrorest) | Brenning 2012 | `ResamplingSpCVCoords`          | `rsmp("spcv-coords")`          |
| Environmental Blocking | [blockCV](https://github.com/rvalavi/blockCV)             | Valavi 2019   | `ResamplingSpCVEnv`             | `rsmp("spcv-env")`             |
| ---                    | ---                                                       | ---           | ---                             | ---                            |
| Repeated Spatial CV    | [sperrorest](https://github.com/giscience-fsu/sperrorest) | Brenning 2012 | `RepeatedResamplingSpCVCoords`  | `rsmp("repeated-spcv-coords")` |
| Repeated Env Blocking  | [blockCV](https://github.com/rvalavi/blockCV)             | Valavi 2019   | `RepeatedResamplingSpCVEnv`     | `rsmp("repeated-spcv-env")`    |

@@

| Name     | Code              | Type    |
| ---      | ---               | ---     |
| ecuador  | `tsk("ecuador")`  | Classif |
| diplodia | `tsk("diplodia")` | Classif |
